Harris County, Texas residents faced several barriers to voter identification access during the 2016 United States election

### 2024-02-13 other/ssrp_report/ssrp_report.qmd
Completed the Data section of the report
Updated the SSRP Report to change the file path of the data
Finalized the report

---
title: "SSRP Report based on *Who Do Voter ID Laws Keep from Voting?* by Fraga and Miller (2022)"
author: "Benny Rochwerg"
format: pdf
editor: visual
---

@@

# Loading the cleaned data
reasons_data_cleaned <- read_csv(here::here("data/replication/reasons_data_cleaned.csv"))
```

>>>>

---
title: "SSRP Report based on *Who Do Voter ID Laws Keep from Voting?* by Fraga and Miller (2022)"
author: "Benny Rochwerg"
date: 02-13-2024
date-format: long
format: pdf
editor: visual
---

#### Preamble ####

# Purpose: Generating an SSRP Report based on the paper "Who Do Voter ID Laws Keep from Voting?" (Fraga and Miller 2022).
# Author: Benny Rochwerg
# Date: February 13, 2024
# Contact: 4321benny@gmail.com
# Pre-requisites: Install the tidyverse (Wickham et al. 2019), patchwork (Pedersen 2024), and here (Müller 2020) packages.
# Run the "01-download_data.R" and "02-data_cleaning.R" files.
```

@@

# Loading the cleaned data
reasons_data_cleaned <- read_csv(here::here("data/reproduction/reasons_data_cleaned.csv"))
```

### 2024-02-13 paper/paper.qmd
Finalized the report

---
title: "Harris County, Texas residents faced several barriers to voter identification access during the 2016 United States election"
author: 
  - Benny Rochwerg
thanks: "Data and code used to generate this report are available here: <https://github.com/bennyrochwerg/voter-id/> \n Replication of three graphs from @voterid is available here: <https://www.socialsciencereproduction.org/reproductions/c0801c33-77d8-4be2-ad60-fa21826856ca/index>"
date: 02-13-2024
date-format: long
abstract: "This report analyzed reasonable impediment declaration (RID) data on barriers to voter identification access in Harris County, Texas during the 2016 United States election. In comparing Harris County to Texas at large, lack of transportation was an overrepresented impediment, hardship was an overrepresented grouped impediment, and hardship among Black RID-filers was overrepresented. Possible contributorsx to these findings, including health and public transit concerns in Harris County, were identified. Future research should examine ways of mitigating these issues, such as enhancing public transit access and improving public health."
format: pdf
number-sections: true
# This method of creating a table of contents was acquired from:
# https://quarto.org/docs/reference/formats/pdf.html
toc: true
bibliography: references.bib
---

@@

Sketches of the data and graphs are available in the GitHub Repository associated with this report.

>>>>

---
title: "Harris County, Texas residents faced several barriers to voter identification access during the 2016 United States election"
author: 
  - Benny Rochwerg
thanks: "Data and code used to generate this report are available here: <https://github.com/bennyrochwerg/voter-id/> \n Replication of three graphs from @voterid is available here: <https://www.socialsciencereproduction.org/reproductions/c0801c33-77d8-4be2-ad60-fa21826856ca/index>"
date: 02-13-2024
date-format: long
abstract: "This report analyzed reasonable impediment declaration (RID) data on barriers to voter identification access in Harris County, Texas during the 2016 United States election. In comparing Harris County to Texas at large, lack of transportation was an overrepresented impediment, hardship was an overrepresented grouped impediment, and hardship among Black RID-filers was overrepresented. Possible contributors to these findings, including health and public transit concerns in Harris County, were identified. Future research should examine ways of mitigating these issues, such as enhancing public transit access and improving public health."
format: pdf
number-sections: true
# This method of creating a table of contents was acquired from:
# https://quarto.org/docs/reference/formats/pdf.html
toc: true
bibliography: references.bib
---

#### Preamble ####

# Purpose: Generating a report titled "Harris County, Texas residents faced several barriers to voter identification access during the 2016 United States election".
# Author: Benny Rochwerg
# Date: February 13, 2024
# Contact: 4321benny@gmail.com
# Pre-requisites: Install the tidyverse (Wickham et al. 2019), patchwork (Pedersen 2024), and here (Müller 2020) packages.
# Run the "01-download_data.R" and "02-data_cleaning.R" files.
```

@@

Sketches of the main data and graphs are available in the GitHub Repository associated with this report.
